%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer (Intern)} % Job title
    {Skoda-Volkswagen} % Organization
    {Chakan, India} % Location
    {Jan. 2020 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented System for data collection, storage, and management of customer orders}
        \item {Created a BOT by using Automation Anywhere Tool which is time and space-efficient.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Pre-Education Program Internship} % Job title
    {EPAM Systems} % Organization
    {Pune, India} % Location
    {Jan. 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I learned about latest technologies like git, github, etc. by online traning and webinars.}
        \item {learned from mentors about basic knowledge of Coding standards, Design patterns, Core java, etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelancer} % Job title
    {DealEasy} % Organization
    {Pune, India} % Location
    {Jul. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a freelancer I am developing websites for the customers using Wordpress.}
        \item {I am also working in Graphics Design, Content Creation, Website SEO and Maintenance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Entrepreneurship} % Job title
    {Shopix} % Organization
    {Baramati, India} % Location
    {Mar. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on idea "To bring all local businesses and customers online on a single platfrom".}
        \item {Learned skills about team building, leadership, multi-tasking, marketing, management, etc.}
        \item {Worked with founders and also got opportunity to pitch our idea in Shark Tank India. }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
